Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/4.ProgammingModel.tex
Bug fix. Added sample code.

Figure~\ref{fig:parallelFor} shows one definition of the Kokkos~\emph{parallel\_for} interface. This interface accepts two template parameters and three function arguments. \emph{ExecPolicy} shapes the iteration space for a particular execution space. Valid template parameter are the~\emph{RangePolicy},~\emph{TeamPolicy},~\emph{MDRangePolicy},~\emph{TeamThreadRange} and~\emph{ThreadVectorRange}. As the name suggests, these policies express how an iteration space is mapped to the underlying hardware. For example, a range policy defines a one dimensional iteration range. A team policy defines a 1D iteration range, each of which is assigned to a thread team. This policy allows the expression of hierarchical parallelism. The second template parameter,~\emph{FuntorType}, represent a functor that implements the~\emph{()-operator} with a matching signature for the given execution policy. The functor can be defined using a C++ class, struct or lambda expression. We would like to highlight that the return semantic of the parallel\_for is defined as \emph{potentially asynchronous}. To guarantee a kernel has finished, a developer should call the fence of the execution space on which the kernel is being executed. Otherwise it depends on the specified execution space and weather this execution space implements a barrier. The semantic of the parallel_for class in Kokkos demonstrates the descriptive nature of the programming model. To the interested reader, the complete programming model specification can be accessed on-line\cite{pub:KOKKOS}. Figure~\ref{fig:abstractions} summarizes patterns and abstractions and structures them by information type in the semantic capture.

>>>>

Figure~\ref{fig:parallelFor} shows one definition of the Kokkos~\emph{parallel\_for} interface. This interface accepts two template parameters and three function arguments. \emph{ExecPolicy} shapes the iteration space for a particular execution space. Valid template parameter are the~\emph{RangePolicy},~\emph{TeamPolicy},~\emph{MDRangePolicy},~\emph{TeamThreadRange} and~\emph{ThreadVectorRange}. As the name suggests, these policies express how an iteration space is mapped to the underlying hardware. For example, a range policy defines a one dimensional iteration range. A team policy defines a 1D iteration range, each of which is assigned to a thread team. This policy allows the expression of hierarchical parallelism. The second template parameter,~\emph{FuntorType}, represent a functor that implements the~\emph{()-operator} with a matching signature for the given execution policy. The functor can be defined using a C++ class, struct or lambda expression. We would like to highlight that the return semantic of the parallel\_for is defined as \emph{potentially asynchronous}. To guarantee a kernel has finished, a developer should call the fence of the execution space on which the kernel is being executed. Otherwise it depends on the execution space where the loop executes and weather this execution space implements a barrier. The semantic of the parallel\_for class in Kokkos demonstrates the descriptive nature of the programming model. To the interested reader, the complete programming model specification can be accessed on-line\cite{pub:KOKKOS}. Figure~\ref{fig:abstractions} summarizes patterns and abstractions and structures them by information type in the semantic capture.

### 2020-01-23 src/5.Backend.tex
Bug fix. Added sample code.

\begin{figure}
\begin{Verbatim}[frame=leftline]

int main(int argc, char* argv[]) {
   Kokkos::initialize(argc,argv);

   int N = atoi(argv[1]);

   Foo foo;

   Kokkos::parallel_for(Kokkos::TeamPolicy<Tag1>(N,Kokkos::AUTO), foo);
   Kokkos::parallel_for("Loop2", Kokkos::TeamPolicy<Tag2>(N,Kokkos::AUTO), foo);

   Kokkos::finalize();
}

\end{Verbatim}
\caption{Declarative parallel programming provides uses pragma annotations to capture semantic information.}
\label{figOMPLike}
\end{figure}

>>>>

\begin{figure}
\begin{Verbatim}[frame=leftline]
int main(int argc, char* argv[]) {
 Kokkos::initialize(argc,argv);
 {
  Foo foo;
  int N = atoi(argv[1]);
  Kokkos::View<int*> a("A",N);  
  Kokkos::parallel_for(Kokkos::RangePolicy<OpenMP>(N), 
     KOKKOS_LAMBDA (const int & i)
  {
  	a(i)=i;
  }); 
 }
 Kokkos::finalize();
}
\end{Verbatim}
\caption{Declarative parallel programming provides uses pragma annotations to capture semantic information.}
\label{figOMPLike}
\end{figure}
